### 2023-11-28 doc/Thesis/chapter/04-experimental.tex
correction transfer until excl characterization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals, substrates, experimental procedures and any used
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
%\td{The experiments can be split into three sections: }
First, the base recipe and the base process settings were explored. 
Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
Finally, the experiments for the optimization were performed.

\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solutions}\label{sec:exp-sol}
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aquatic solution).
The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic solution}\label{sec:exp-sol-aq}
\gls{zrpro} was added to \gls{acac} while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to \gls{ipo} and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the resulting layer. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the other solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce anything near homogeneous layers. 
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
Five different concentrations of the buthanolic solutions were prepared. 
Not all chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
The \gls{1f} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar with 
but higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Different solvents (Butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\gls{pso} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
The main differences between the used recipe and the recipe mentioned by \cite{Hu2016} were 
precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Doctor blading}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar 
coater. On two opposing edges adhesive tape was applied to create a valley in between. After the 
layer was applied and dried the tape was removed and the substrate treated with heat.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates 
were doctor bladed with 
an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and did not substantially alter the results.
For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape to increase the suction intensity at the remaining ones (see figure~\ref{fig:eric}
After setting the temperature of the heating plate to 
\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The doctor bladed substrate was transferred to the \SI{200}{\celsius} heating plate and 
rested on there for \minutes{5}. 
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calcination}\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This heating procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{materials section and sources (incl. purities is missing!}
In this section the used chemicals, substrates, experimental procedures and any used
\td{equipment (what do you mean?)} are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
%\td{The experiments can be split into three sections: }
First, the base recipe and the base process settings were explored. 
Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
Finally, the experiments for the optimization were performed.

\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{ito} plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{fto} plates (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Precursor Solutions}
\label{sec:exp-sol}
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar~et~al.~\cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water} (aquatic solution).
The second recipe - adopted from Hu~et~al.~\cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh} (buthanolic solution).

\iffalse
\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-aq.png}
		\label{fig:sol-aq}
		\caption{Aquatic solution}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[height=0.8\textwidth]{Pics/sol-bu.png}
		\label{fig:sol-bu}
		\caption{Buthanolic solution}
	\end{subfigure}
	\label{fig:sol}
	\caption{Aquatic and buthanolic solution with magnetic stirring bars in beaker glass sealed with Parafilm} 
\end{figure}
\iffalse

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic Precursor Solutions}\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to \td{influence the resulting layer (in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \td{other solution (which? NOT CLEAR!)} and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory.

The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
\td{Different} solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before the 
\td{particle swarm optimisation} started - the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%DB          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Doctor blading}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated \td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in 
\SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate
had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where 
underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape to increase the suction intensity at the remaining ones \td{(see figure~\ref{fig:eric}).
After} setting the temperature of the heating plate to 
\SI{200}{\celsius}, the temperature of the vacuum plate (room temperature, \SI{40}{\celsius}, 
\SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) and the 
\gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the 
liquid evenly. After evaporation of the solution, the vacuum was turned off, the 'blade 
pusher' was put into initial position, the blade was removed and excess solution 
was removed from the plate with a wipe. 
The coated substrate was \td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\micro\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calcination of Films}\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of \td{circa (and how do you optimze ca?)} \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This heating procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization}
\td{All \gls{sem} micrographs were taken with a Zeiss Supra 40. (conditions? were samples sputtered etc...)}
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.
